Converting 'LaTeX' 'R Journal' Articles into 'RJ-web-articles

### 2023-06-18 texor.Rmd
A short para on pandoc usage

>>>>

### Pandoc Usage

Pandoc is a versatile document conversion program written in Haskell that is core
to numerous documentation systems, including Rmarkdown and Quarto. Pandoc first 
converts a document into an abstract syntax tree. From this, it can convert to a
different format, including custom ones. Although creating bespoke writers/readers
in Lua can be challenging, pandoc includes filters that allow users to customise 
the output generated based on matching patterns plus some logic to modify them.

The Texor package uses these filters heavily, even for simple tasks like choosing
which supporting figures to copy. A lua filter constructs a list of image paths, 
writes it to an intermediate file and feeds them to the Texor package.

This was one of the earliest and most basic Lua filters, and it was part of the 
texor package:

```Lua
function Div(el)
    if el.classes[1] == 'thebibliography' then
        return { }
    end
end
```

Above filter reads the abstract syntax tree and filters out all the Div elements.
Then it looks for the class "thebibliography." It turns out that this Div element 
contains the LaTeX bibliographic records, which usually appear at the very end 
of papers. We don't need this portion in the article with the "RJ-web-article" 
layout,  given its inclusion as meta-data in the footer.
